Estudio variabilidad estructural proteica

### 2016-05-23 AllFamilys.Rmd
cambios 23/05/2016

---
title: "MSDi for all families together"
author: "Maria Laura Marcos"
output: html_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

>>>>

---
title: "MSDi for all families together"
author: "Maria Laura Marcos"
output: pdf_document
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(warning = FALSE, echo = FALSE, message = FALSE)
```

### 2016-05-23 MultipleReportAllBetas.Rmd
cambios 23/05/2016

}

>>>>

# Write pdb files for MSDi.
pdbs.fname <- file.path(data.dir, paste(family, "_coordinates.pdb", sep = ""))
pdb = ReadCA(pdbs.fname, as.character(chain.p.ref))
xyz.calpha = pdb$xyz.calpha

MSDi.fit.pdb <- vec2resno(as.vector(MSDi.fit), sort(rep(1:ncol(xyz.calpha),3)))
write.pdb(xyz = c(xyz.calpha), b = MSDi.fit.pdb, file = file.path(out.dir, paste(family, "_", p.ref, "_beta_", beta, ".pdb", sep = "")))

MSDi.exp.pdb <- vec2resno(as.vector(exp.smooth.norm.MSDi), sort(rep(1:ncol(xyz.calpha),3)))
write.pdb(xyz = c(xyz.calpha), b = MSDi.exp.pdb, file = file.path(out.dir, paste(family, "_", p.ref, "_exp", ".pdb", sep = "")))
}
